Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2019-07-21 nir_companions.tex
update wavelength masking

\subsection{Wavelength masking}
We apply several wavelength masks to remove wavelength regions from which we cannot extract information.
Firstly, regions near the edges of each detector where the wavelength solution is extrapolated outside of the calibrating telluric lines are removed, reducing the effective size of each detector by about \(10\) per cent or \(\sim\)100~pixels.

Secondly, we mask out any remaining artefacts present in the spectra and the centres of deep telluric lines where telluric correction was not corrected properly, sometimes resulting in ``emission-like'' peaks in the corrected spectrum. These factors combined result in masking out around a further 10 per cent of the observed spectra.

In Sect.~\ref{sec:results} we also apply a further wavelength restriction to mask out regions where there is a large mismatch between the observed spectrum and the closest synthetic spectra to the host. This significantly restricts the wavelength span utilized for that purpose to around only 43 per cent and the masked regions are visible in Fig.~\ref{fig:visualinspection-hd2118471}.

{\bl The observations were gathered having in mind the application of a differential subtraction method~\citep[e.g.][]{ferluga_separating_1997, kostogryz_spectral_2013}. However with the small time separation of the observations and long orbital periods the spectral shift of the companions' lines result in an insufficient separation to detect the spectrum of the companion spectrum.
}

>>>>

\subsection{Wavelength masking}
Several wavelength masks are applied to remove wavelength regions from which we cannot extract spectral information.
Firstly, regions near the edges of each detector where the wavelength solution is extrapolated outside of the calibrating telluric lines were removed, reducing the effective size of each detector by about \(10\) per cent or \(\sim\)100~pixels.

Secondly, any remaining artefacts present in the spectra were masked out and the centres of deep telluric lines where telluric correction was not corrected properly. These sometimes resulted in ``emission-like'' peaks in the corrected spectrum. These two factors resulted in masking out around a further 10 per cent of the observed spectra.

In Sect.~\ref{sec:results} a further wavelength restriction is used to mask out regions where there is a large mismatch between the observed spectrum and the closest synthetic spectra for the host star. This significantly restricts the wavelength span utilized to around only 43 per cent. The masked regions are shown as the shaded areas in Fig.~\ref{fig:visualinspection-hd2118471}.
